### 2017-07-17 main.tex
Add raw tiff figures. They will be rescaled shortly.

\begin{figure}
  % Width 8, height 3, font 120%
  \includegraphics[width=\textwidth]{Fig3}
  %\includegraphics[width=\textwidth]{accuracies-2hidden}

@@

Syllable choice impacts detector performance, but despite the variety
of syllables shown here, performance was stable across syllables.
\fig{fig:TimingVsSyllable} shows measured timing data for lny64's test
syllables for the Swift+serial detector compared to the ideal, with
$t_{\textrm{fft}}=1.5$ ms.  Given the variety of the test syllables,
the variability is surprisingly low, and is summarised here with 95\%
confidence intervals (with n=6):
\vspace{8pt}\par\noindent
\begin{tabular}{r|cc}
  Detector & Latency & Jitter \\ 
  \hline   Ideal & $-0.8\pm 0.3$ ms & $2.1\pm 0.1$ ms \\
  Swift+serial & $0.0\pm 0.6$ ms & $2.0\pm 0.1$ ms
\end{tabular}
\vspace{8pt}\par\noindent
The negative latency is due to the way in which the network responds
to the song through time: as the recognition region looks increasingly
similar to the trained match, the network's evaluation of similarity
rises, and will generally cross the triggering threshold before it
reaches its maximum value.  A heuristic as simple as triggering at an
apparent turning point after crossing the threshold might improve
timing consistency at the expense of latency, but we did not test this.

@@

We compared latency and jitter across our different detector
implementations for the $\delta$-syllable and lny64's $t^*_4$, again with
$t_\mathrm{fft}=1.5$ ms.  Results are as follows:
\vspace{8pt}
\begin{tabular}{l|c|c|c|c}
  & \multicolumn{2}{c}{$\delta$-syllable} & \multicolumn{2}{c}{Bird: $t^*_4$} \\
  Detector & Latency (ms) & Jitter (ms) & Latency (ms) & Jitter (ms) \\
  \hline
  Ideal & 0.66 & 0.38 & -1.0 & 2.0 \\
  LabVIEW & 1.5 & 0.69 & -0.18 & 2.4 \\
  Swift+serial & 0.88 & 1.6 & -0.075 & 2.0 \\
  Swift+audio & 5.9 & 2.6 & 1.2 & 4.9 \\
  MATLAB+serial & 8.1 & 2.3 & 3.8 & 2.0 \\
  MATLAB+audio & 13 & 5.9 & 8.4 & 5.9
\end{tabular}
\vspace{8pt}\par\noindent
These data are also plotted in \fig{fig:TimingVsDetector}, and
\fig{fig:timing} gives a more detailed view of what the timing curves
look like for the five implementations of our detector on $t^*_4$.

@@

\section{Acknowledgments}
We would like to thank Winthrop F.~Gillis, William A.~Liberti, and Sanne Moorman for
their improvements to the draft.  This work was funded by NIH grants
5R01NS089679-02 and 5U01NS090454-02.  The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

>>>>

\begin{figure}
  % Width 10, height 4, font 100%
  \includegraphics[width=\textwidth]{Fig3}

@@

Syllable choice impacts detector performance, but despite the variety
of syllables shown here, performance was stable across syllables.
\fig{fig:TimingVsSyllable} shows measured timing data for lny64's test
syllables for the Swift+serial detector compared to the ideal, with
$t_{\textrm{fft}}=1.5$ ms.  Given the variety of the test syllables,
the variability is surprisingly low, and is summarised in
Table~\ref{table:TimingVsSyllable}.

\begin{table}
  \begin{tabular}{r|cc}
    Detector & Latency & Jitter \\ 
    \hline   Ideal & $-0.8\pm 0.3$ ms & $2.1\pm 0.1$ ms \\
    Swift+serial & $0.0\pm 0.6$ ms & $2.0\pm 0.1$ ms
  \end{tabular}
  \caption{Latency and jitter variability (95\% confidence) for lny64's six test syllables.}
  \label{table:TimingVsSyllable}
\end{table}

The negative latency is due to the way in which the network responds
to the song through time: as the recognition region looks increasingly
similar to the trained match, the network's evaluation of similarity
rises, and will generally cross the triggering threshold before it
reaches its maximum value.  A heuristic as simple as triggering at an
apparent turning point after crossing the threshold might improve
timing consistency at the expense of latency, but we did not test this.

@@

We compared latency and jitter across our different detector
implementations for the $\delta$-syllable and lny64's $t^*_4$, again with
$t_\mathrm{fft}=1.5$ ms.  Results are shown in Table~\ref{table:TimingVsDetector}.
These data are also plotted in \fig{fig:TimingVsDetector}, and
\fig{fig:timing} gives a more detailed view of what the timing curves
look like for the five implementations of our detector on lny64's $t^*_4$.

\begin{table}
  \begin{tabular}{l|c|c|c|c}
    & \multicolumn{2}{c}{$\delta$-syllable} & \multicolumn{2}{c}{lny64: $t^*_4$} \\
    Detector & Latency (ms) & Jitter (ms) & Latency (ms) & Jitter (ms) \\
    \hline
    Ideal & 0.66 & 0.38 & -1.0 & 2.0 \\
    LabVIEW & 1.5 & 0.69 & -0.18 & 2.4 \\
    Swift+serial & 0.88 & 1.6 & -0.075 & 2.0 \\
    Swift+audio & 5.9 & 2.6 & 1.2 & 4.9 \\
    MATLAB+serial & 8.1 & 2.3 & 3.8 & 2.0 \\
    MATLAB+audio & 13 & 5.9 & 8.4 & 5.9
  \end{tabular}
  \caption{Latency and jitter for each of our detector implementations on the synthetic $\delta$-syllable and on syllable $t^*_4$ from lny64.}
  \label{table:TimingVsDetector}
\end{table}

@@

\section{Acknowledgments}
We would like to thank Winthrop F.~Gillis, William A.~Liberti, and Sanne Moorman for
their improvements to the draft.
%  This work was funded by NIH grants
%5R01NS089679-02 and 5U01NS090454-02.  The funders had no role in study %design, data collection and analysis, decision to publish, or preparation of the %manuscript.
